Regression Cube Analysis of Cohort Study Data

### 2015-06-21 draft.tex
added missing papers

>>>>

\magenta{
Guo et al.~\cite{Guo} presented a multi-space visualizations to find linear relationships in the data with focus on extracting groups, which fit best.
%%
The data space is visualized using a scatter plot matrix.
%%
Linear models are calculated by defining dependent and independent features.
%%
The model view allows for assessing different models by color coding distances to the line-of-fit.
%%
The model-parameters can then be fine-tuned using line graphs, histograms and model projections.
%%
The paper is focused on finding and tuning a model for a specific relationship, while we search for models w.r.t. all combinations in the data set.
}

\magenta{
M\"{u}hlbacher et al.~\cite{Muehlbacher} provide a framework for qualitative analyses of relationships and ranking features for numerical target features with regression models.
%%
A view for single-relationships with the target and single features as well as a matrix-plot for feature combinations are used to depict models of interest.
%%
The visualization allows to assess different model complexities.
%%
Existing regression models can be validated and compared using 3D views and 2D slice-views.
%%
We employ the same steps by assessing single-relationships with the target and providing a overview over combinations.
%%
M\"{u}hlebacher et al. focus on a smaller number of features, which can be assessed in more detail, yielding a plot-matrix view, while we cover more features by abstracting the models using color coded regression metrics.
%%
We also take categorical targets and regression formula inputs into account.
%%
Existing regression models can be validated and compared using 3D views and 2D slice-views.
}
